\capitulo{6}{Related works}

\section{Web Thoth}
Web Thoth~\cite{web_thoth} is the final project presented by Ismael Ramos Pérez, one of the tutors for this project, as part of his degree in Computer Engineering. It was created in 2016 with the help of tutors Dr. César Ignacio García Osorio and Dr. Álvar Arnaiz González. It is composed of a website that helps users learn lexical analysis algorithms by showing explanations and examples. With its goal being of similar nature to the one of this project, its main influences lie in the layout and overall functionality of the presented website. E.g., one of its main features, the step-by-step simulation of the presented algorithms, has had a significant influence on this project.

\section{SVM demo}
The Interactive demo of Support Vector Machines (SVM)~\cite{svm_demo} is a web application that lets the user input data points of either one of two classes on a canvas which results in the creation of hyperplanes that best separate the two classes. Based on the user's input and the adjustable parameters, the calculation and display of the hyperplanes changes dynamically. That dynamic change in data is also implemented in this project.

\section{A Visual and Interactive Look at Basic Neural Network Math}
This work's~\cite{neural_network_math_demo} goal is to teach the user the concepts of basic neural network math. It includes intuitive visual representations of a neural network, its elements and calculations, and the ReLU function. Additionally, the user can change some of the input data, to which the application responds with visual cues as to what kind of changes were made. This dynamic visualization of changing data, again, has been an influence on this project.